---
title: "Prepforfinal"
author: "Yuhan Wu"
date: "6/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(dplyr)
library(plotly)
library(gganimate)
library(gifski)
library(png)
library(patchwork)
library(gapminder)

```

```{r,echo=FALSE}


raw_data_BO <- read.csv("BOXRSA.csv")
raw_data_NY <- read.csv("NYXRSA.csv")
raw_data_SF <- read.csv("SFXRSA.csv")

data_BO <- raw_data_BO %>%
mutate(City="Boston") %>%
mutate(Data= BOXRSA)

data_NY <- raw_data_NY %>%
  mutate(City="New York")%>%
  mutate(Data= NYXRSA)

data_SF <- raw_data_SF %>%
  mutate(City ="San Francisco")%>%
mutate(Data= SFXRSA)

clean_data <-bind_rows(data_BO,data_NY,data_SF)
```

```{r,echo=FALSE}
data_final <- clean_data %>%
select(DATE,Data,City)%>%
  group_by(City) 
```

```{r}
data_plotly <- data_final%>%
ggplot(mapping=aes(x = DATE,y=Data,color=City,group=1, text = paste("Date:",DATE, "\n")))+
  geom_line()+
  scale_x_discrete(breaks=12)+
  labs(title="Housing Price fluctuation between 1984 and 2021 of three Cities", subtitle = "San Francisco endured the greatest decline in year 2008",x="Time (1987-2021)",y="Case-Shiller index")

   ggplotly(data_plotly, tooltip = "text")

```

clean_data %>%
  filter(region == "TotalUS") %>%
  ggplot(aes(Date, `Total Volume`/1000000, color = type))+
  geom_line()+
  transition_reveal(Date)+
  labs(title = "The Volume of Avocados Sold Over Time by Type of Fruit",
      subtitle = "The overall volume of avocados has significant fluctuations depending on the type of fruit",
        y = "Total Volume in Millions", color = "Type of Avocado")+
    view_follow(fixed_y = TRUE)
    
    
library(tidyverse)




